Nanophotonic Computational Design

### 2013-03-03 paper/paper.tex
Minor.
Closer

\documentclass[letterpaper,10pt]{article}
\usepackage{graphicx}
\usepackage{opex3}
\usepackage{amsmath,amssymb}
\begin{document}
\title{Nanophotonic Computational Design}
\author{Jesse Lu$^\ast$ and Jelena Vu\v{c}kovi\'{c}}
\address{Stanford University, Stanford, California, USA.}
\email{jesselu@stanford.edu}

@@

\section{Method}

>>>>

\documentclass[letterpaper,10pt]{article}
\usepackage{graphicx}
\usepackage{opex3}
\usepackage{amsmath,amssymb}
\input defs.tex
\begin{document}
\title{Nanophotonic Computational Design}
\author{Jesse Lu$^\ast$ and Jelena Vu\v{c}kovi\'{c}}
\address{Stanford University, Stanford, California, USA.}
\email{jesselu@stanford.edu}

@@

\section{Method}
% Problem statement 
In order to produce designs which utilize the full parameter space,
    and are based solely on the user's performance specification,
    we formulate the design problem in the following way:
\begin{subequations}\begin{align}
    \minimize & \sum_i^M \|A_i(z)x_i - b_i\|^2 \\
    \subto & \alpha_{ij} \le |c_{ij}\T x_i| \le \beta_{ij}, \quad
        \text{for $i = 1, \ldots, M$ and $j = 1, \ldots, N_i$} \\
        &   z_\text{min} \le z \le z_\text{max}
\end{align} \label{problem}\end{subequations}

The explanation for the various terms in \eqref{problem} follows:
\begin{enumerate}
\item 
    $A_i(z)x_i - b_i$ is the \emph{physics residual} for the $i$th mode.
    That is to say, $A_i(z)x_i - b_i$ represents the underlying physics
        of the problem; namely, the electromagnetic wave equation
        \mbox{$(\nabla\times\mu_0^{-1}\nabla\times - \omega_i^2 \epsilon) E_i 
            +i \omega_i J_i $}.

    The specific substitutions used in order to transform
        \BE (\nabla\times\mu_0^{-1}\nabla\times - \omega_i^2 \epsilon) E_i 
            +i \omega_i J_i  \quad\longrightarrow\quad A_i(z)x_i - b_i \EE
        are
    \BI $E_i \to x_i$,
    \I  $\epsilon \to z$,
    \I  $\nabla\times\mu_0^{-1}\nabla\times - \omega_i^2 \epsilon \to A_i(z)$, and
    \I  $ -i\omega_i J_i \to b_i$.  \EI

    In contrast to typical schemes for optimizing physical structures,
        our formulation actually allows for non-zero physics residuals;
        which can be deduced since $A_i(z)x_i-b_i=0$ is not a hard constraint.
    Instead, this formulation is what we call an \emph{objective-first} % Ref
        formulation in that the \emph{design objective} (explained below)
        is prioritized above satisfying physics.

\item
    The (field) design objective consist of 
        the constraint $\alpha_{ij} \le |c_{ij}\T x_i| \le \beta_{ij}$.
    Physically, this constraint describes 
        the performance specification of the device 
        via a series of field overlap integrals 
        at various output ports of the device.
    Specifically, the $c_{ij}\T x_i$ terms represents an overlap integral between
        the E-field of the $i$th mode ($x_i$)
        with an E-field of the user's choice ($c_{ij}$),
        where the additional subscript $j$ allows the user
        to include multiple such fields.

    The amplitude of the overlap integral is then forced

\end{enumerate}
% how we solved it
% Maxwell
